Deep mutational scanning of an H3 hemagglutinin can inform evolutionary forecasting of human H3N2 influenza virus

### 2017-11-27 paper/manuscript.tex
clean up title page and add title suggestion

\title{TITLE}

\author
{Juhye M. Lee$^{1,3,4,\dagger}$, John Huddleston$^{2,4,\dagger}$, Michael B. Doud$^{1,3,4}$, Kathryn A. Hooper$^{1,4}$, Trevor Bedford,$^{2}$ and Jesse D. Bloom$^{1,3,5*}$\\
\\
\scriptsize{$^1$Basic Sciences and Computational Biology Divisions, Fred Hutchinson Cancer Research Center}\\
\scriptsize{$^2$Vaccine and Infectious Diseases Division, Fred Hutchinson Cancer Research Center} \\
\scriptsize{$^3$Department of Genome Sciences and $^4$Medical Scientist Training Program, University of Washington} \\
\scriptsize{$^5$Department of Molecular and Cellular Biology, University of Washington} \\
\scriptsize{Seattle, WA, USA} \\
\scriptsize{$^{\dagger}$These authors contributed equally} \\
\scriptsize{$^*$Correspondence: \href{jbloom@fredhutch.org}{jbloom@fredhutch.org}}
}

>>>>

\title{Deep mutational scanning of an H3 hemagglutinin can inform evolutionary forecasting of human H3N2 influenza virus}

\author{
Juhye M. Lee$^{1,4,5,\dagger}$ \and 
John Huddleston$^{2,6,\dagger}$ \and 
Michael B. Doud$^{1,4,5}$ \and 
Kathryn A. Hooper$^{1,6}$ \and
Trevor Bedford,$^{2,3}$ \and 
Jesse D. Bloom$^{1,3,4*}$
\\
\scriptsize{$^1$Basic Sciences Division, $^2$Vaccine and Infectious Diseases Division, and $^3$Computational Biology Program,} \\
\scriptsize{Fred Hutchinson Cancer Research Center, Seattle, WA, USA} \\
\scriptsize{$^4$Department of Genome Sciences, $^5$Medical Scientist Training Program, and $^6$Molecular and Cellular Biology Program,} \\
\scriptsize{University of Washington, Seattle, WA, USA} \\
\scriptsize{$^{\dagger}$These authors contributed equally} \\
\scriptsize{$^*$Correspondence: \href{jbloom@fredhutch.org}{jbloom@fredhutch.org}}
}
